---
title: "Developing Data Products Week4"
author: "Shailesh Parab"
date: "29/03/2020"
output: ioslides_presentation
widescreen: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Developing Data Products Assignment

This project is created as a part of Developing Data Products Week 4 assignment.

Highlights

1. Project contains Shiny Application for predicting hight of next gen based on parents hight

2. Project uses many forms of inputs

3. Project uses interactive chart for showing output.

4. Project conains Server.R and UI.R files

## How to use the application
Data set used for project : Galton Family

Use the slider for increasing/decreasing hight in CM for Father and Mother

Selet the child number from between 1 to 5

Select gender of child

Graph is auto populated based on the data selection

## Galton Families Dataset

Glimps of GaltonFamilies dataset. 

```{r summary, warning = FALSE}
library(HistData)
data(GaltonFamilies)
summary(GaltonFamilies)
```

## Plot
Below is the chart displaying data used in project.

```{r plot}
library(HistData)
data(GaltonFamilies)
intMidP <- GaltonFamilies$midparentHeight*2.54
intChH <- GaltonFamilies$childHeight*2.54
plot(jitter(intChH) ~ intMidP,xlab="Average Height of the Parents (in cm)",ylab="Height of the Child (in cm)",main="Scatterplot of Galton Family Data",pch=19,frame.plot=FALSE,col=ifelse(GaltonFamilies$gender=="female", "red", "blue"))
legend(65,80,pch=c(19,19),col=c("pink","light blue"),c("female", "male"),bty="o",cex=.5)
```